%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Md Abdul Hasib 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Md Abdul Hasib} % Your name
\address{62/4/A South Mugda, Dhaka, Bangladesh} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{+880-1917187787 \\ abdulhasibsazzad@gmail.com} % Your phone number and email
%\address{https://imsazzad.github.io/}
%\address{https://www.hackerrank.com/SazzadBuet08}


\begin{document}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bangladesh University of Engineering and Technology, Dhaka} \hfill {\em 2009 - 2014} 
\\ B.Sc. in Computer Science and Engineering.\hfill { CGPA: 3.48 }

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}



%----------------------------------------------------------------------------------------
%	Certification SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Certifications}

{\bf Deep Learning Specialization} \hfill {\em July 2018 - Now } 
\\ \href{https://www.coursera.org/account/accomplishments/specialization/TLSQP268HYTN}{See credential}\hfill { Coursera }

{\bf Certified ScrumMaster® (CSM®)} \hfill {\em July 2016 - Now } 
\\ \href{http://bcert.me/sufosajdm}{See credential}\hfill { Scrum Alliance }

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Machine Learning \ & Traditional ML, Deep Learning, Natural Language Processing(NLP) \\
Language & Java, Python, C++, C, SQL, Javascript \\
Tools \& Technologies & MySQL, Html, CSS, MongoDB, Hadoop, Linux, PL/SQL, Jenkins, AWS, \\
&  Oracle, Git, Google Colab, Jupyter Notebook, Jira(Admin), Latex \\
Framework \ & Ruby on Rails, TensorFlow, Keras, ReactJS \\
\end{tabular}

\end{rSection}
%\newpage


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
\begin{rSubsection}{deeplearning.ai}{Jan 2020 - Now}{Consultant}{}
\item Reviewing the upcoming courses at deeplearning.ai 
\end{rSubsection}

\begin{rSubsection}{Infolytx Inc, Dhaka}{April 2019 - Now}{Staff Software Engineer / Machine Learning Engineer }{} 
\item Leading machine learning Team and AI projects to articulate and disseminate Data science knowledge as well as domain knowledge to the team members.
\item Structured, unstructured clinical content such as EHR by extracting and inferring medical terms such as findings, tests, procedures, diseases, etc using NLP techniques
\item Implemented Object Detection Algorithm to classify and localize an object in an image.
\end{rSubsection}

\begin{rSubsection}{Infolytx Inc, Dhaka}{November 2016 - March 2019}{Senior Software Engineer}{}

\item Implemented the cohort identification system for the clinical trial in the N2C2 competition of Harvard Medical School. Got a position in TOP 5 in competition and were invited to the present the work with AMIA in San Francisco, California. 
\item Detected the type of breast cancer based on the SEER dataset using traditional machine learning and deep learning techniques.
\item Implemented the application to monitor the ambulatory status of residents using Deep Learning Techniques(LSTM, Rule-Based) 
\item Natural language processing in electronic medical records (Java)
\item Developed web services, APIs(Java, Python), frontend in ReactJS

\end{rSubsection}

\begin{rSubsection}{Infolytx Inc, Dhaka}{September 2015 - October 2016}{Software Engineer}{}
\item Worked with Apriori algorithm, KNN, SVM, and different rule-based techniques to solve different machine learning solutions.
\item Worked with UMLS dictionaries and HL7 standards, large clinical data sets such as EHR in MongoDB
\end{rSubsection}
%\newpage
\begin{rSubsection}{Nascenia Limited, Dhaka}{August 2014 - August 2016}{Junior Software Engineer}{}

\item Developed Web application on Ruby on rails solely as well as a team player from the initial requirement gathering to design, coding, testing, documentation,implementation and client handling.
\item Worked with the application server, web server, and Jenkins server.
\item Handled and provided API services. 
\item Took Technical Session on Git, Clean Code, Active Record Query 
\end{rSubsection}

\end{rSection}


%	Academic Achievements
%----------------------------------------------------------------------------------------

%\begin{rSection}{Academic Achievements} 
%\item Received government scholership both in S.S.C  and H.S.C
%\end{rSection}

%----------------------------------------------------------------------------------------
%	Honors and Awards SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors \& Awards}

{\bf Award-Winning work with the N2C2 Challenge}  \hfill {\em Infolytx Inc - November 2018} 


{\bf Taking leadership by the horns} \hfill {\em Infolytx Inc - January 2018} 

{\bf Outstanding Contributions to the cognitive chatbot work} \hfill {\em Infolytx Inc - December 2017} 

{\bf Outstanding Adoption of New Technologies and the\\ Establishment of Significant Capabilities in Data Analytics} \hfill {\em Infolytx Inc - August 2016} 

{\bf Extraordinary Software Developer} \hfill {\em Infolytx Inc - January 2016} 

{\bf Government Scholarship} \hfill {\em Education Board -March 2009} 

\end{rSection}

%\newpage

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
\item Attended a workshop to present project N2C2 \& DEEP VISION at ACI Limited, Dhaka in 2019.
\item Finalist of Inter Departmental Cricket Competition 2014.
\item Was a member of the Bishwo Shahitto Kendro from 2004 to 2006.
\item Was a member of Bangladesh Scouts from 2006-2007.
\item  Participated in Intra Software Cricket tournament in 2017 organized by all software companies, Dhaka.
\item Won a cell phone in a coaching center after solving a hard math problem in 2005.

\end{rSection}


\begin{rSection}{Social Profile}
\item[•] \href{https://imsazzad.github.io/}{Website}
\item[•] \href{https://www.linkedin.com/in/md-abdul-hasib-sazzad-19b88099/}{LinkedIn}
\item[•] \href{https://github.com/imsazzad/}{Github}
\item[•] \href{https://www.hackerrank.com/SazzadBuet08}{HackerRank}
\item[•] \href{https://www.kaggle.com/sazzadabdulhasib}{Kaggle}
\end{rSection}

\end{document}
%\address{github.com/imsazzad}
%\address{https://www.hackerrank.com/SazzadBuet08}
